---
title: "IS415-Geo-Covid"
author: "IS415 Group 6 by: Ivy, Shermin, Jasky"
date: "10/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

# Introduction

# Getting Started
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
packages = c('sp','tidyverse', 'sf',  'rgdal','spatstat', 'spatstat', 'raster', 'maptools', 'rgeos','dplyr', 'tmap', 'ggplot2', 'spdep', 'lubridate')

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

# Import data
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
hk_district <- st_read(dsn = "data/geospatial", layer = "HKDistrict18")
hk_region <- read.csv("data/geospatial/Hong_Kong_18_Districts.csv")
hk_location <- st_read(dsn = "data/geospatial", layer = "hong_kong_location")
pop_district_2016 <- read_csv("data/aspatial/Population by District Council and Year.csv")
pop_sex <- read.csv("data/aspatial/population-by-sex.csv")
confines_qc <- read_csv("data/aspatial/no_of_confines_by_types_in_quarantine_centres_eng.csv")
occupancy_qc <- read_csv("data/aspatial/occupancy_of_quarantine_centres_eng.csv")
indv_caseinfo <- read_csv("data/aspatial/enhanced_sur_covid_19_eng.csv")
reported_cases_by_country <- read_csv("data/aspatial/countries_areas_have_reported_cases_eng.csv")
testing_done_mth <- read_csv("data/aspatial/statistics_on_covid_19_testing_cumulative.csv")
cases_location <- read_csv("data/aspatial/building_list_eng.csv")
```


# Data Cleaning


## HK District and Region
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
hk_map <- cbind(hk_district, hk_region$REGION) %>%
  rename('REGION' = 'hk_region.REGION')
```

## Population by Sex in 2020
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
pop_sex_2020 <- pop_sex %>%
  filter(year == 2020) %>%
  mutate('total' = `male` + `female`)
```

## No. of Confines by Types in Quarantine Centres

### Check for duplicates
```{r}
duplicated(confines_qc)
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
confines_qc$`As of date` <- as.Date(confines_qc$`As of date`, "%d/%m/%y")
confines_qc$`As of month` <- format(confines_qc$`As of date`, "%m")


confines_qc_cumul_close <- confines_qc %>%
  dplyr::select("As of date", "Cumulative number of close contacts of confirmed cases")
  
confines_qc_cumul_nonclose <- confines_qc %>%
  dplyr::select("As of date", "Cumulative number of non-close contacts")

confines_qc_current_close <- confines_qc %>%
  dplyr::select("As of date", "Current number of close contacts of confirmed cases")

confines_qc_cuurent_nonclose <- confines_qc %>%
  dplyr::select("As of date", "Current number of non-close contacts")
```


### Line graph

#### Cumulative number of close contact

```{r}
confines_cumul_close_line <- 
  ggplot(confines_qc_cumul_close, aes(x = `As of date`, y = `Cumulative number of close contacts of confirmed cases`)) +
  geom_line()

confines_cumul_close_line
```

#### Cumulative number of non-close contact

```{r}
confines_cumul_nonclose_line <- 
  ggplot(confines_qc_cumul_nonclose, aes(x = `As of date`, y = `Cumulative number of non-close contacts`)) +
  geom_line()

confines_cumul_nonclose_line
```

#### Current number of close contact

```{r}
confines_current_close_line <- 
  ggplot(confines_qc_current_close, aes(x = `As of date`, y = `Current number of close contacts of confirmed cases`)) +
  geom_line()

confines_current_close_line
```

#### Current numebr of non-close contacts

```{r}
confines_current_nonclose_line <- 
  ggplot(confines_qc_cuurent_nonclose, aes(x = `As of date`, y = `Current number of non-close contacts`)) +
  geom_line()

confines_current_nonclose_line

```


## Total No. of Reported Cases Daily in HK
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
hk_reported_cases <- reported_cases_by_country %>%
  filter(`Countries/areas` == 'Hong Kong Special Administrative Region') %>%
  
```



# EPSG:2326
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
hk_map_2326 <- st_set_crs(hk_map, 2326)
hk_location_2326 <- st_set_crs(hk_location, 2326)
```

## indv_caseinfo

###Frequency of Covid'19 Cases based on Gender
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
freq_genderM <- indv_caseinfo %>%
  filter(Gender == 'M') %>%
  count(Gender) %>%
  rename(count = n)

freq_genderF <- indv_caseinfo %>%
  filter(Gender == 'F') %>%
  count(Gender) %>%
  rename(count = n)

freq_gender <- rbind(freq_genderM, freq_genderF)

ggplot(freq_gender, aes(x=Gender, y=count, fill=Gender)) + geom_bar(stat='identity', width = 0.7) + theme_minimal() + geom_text(aes(label=count), vjust=1.6, color="white", size=3.5)

```


###Confirmed Cases by Date
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
indv_caseinfo$`Report date` <- as.Date(indv_caseinfo$`Report date`, "%d/%m/%Y")

confirm_cases <- indv_caseinfo %>%
  mutate(confirm_count = 1) %>%
  dplyr::select('Case no.', 'Report date', 'confirm_count') %>%
  group_by(`Report date` = floor_date(`Report date`, "month")) %>%
  summarise(confirm_count = sum(confirm_count)) 

confirm_cases <- within(confirm_cases, conf_cumul <- cumsum(confirm_count))
```

###Death Cases by Date
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
death_cases <- indv_caseinfo %>%
  filter(indv_caseinfo$`Hospitalised/Discharged/Deceased` == 'Deceased') %>%
  mutate(death_count = 1) %>%
  dplyr::select('Case no.', 'Report date', 'death_count') %>%
  group_by(`Report date` = floor_date(`Report date`, "month")) %>%
  summarise(death_count = sum(death_count))

death_cases <- within(death_cases, dth_cumul <- cumsum(death_count))
```

###Recovered Cases by Date
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
recovered_cases <- indv_caseinfo %>%
  filter(indv_caseinfo$`Hospitalised/Discharged/Deceased` == 'Discharged') %>%
  mutate(recovered_count = 1) %>%
  dplyr::select('Case no.', 'Report date', 'recovered_count') %>%
  group_by(`Report date` = floor_date(`Report date`, "month")) %>%
  summarise(recovered_count = sum(recovered_count))

recovered_cases <- within(recovered_cases, recov_cumul <- cumsum(recovered_count))
```

###Combine confirmed, death and recovered count cases
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
confdth_cases <- left_join(confirm_cases, recovered_cases, by="Report date")
combined_count <- left_join(confdth_cases, death_cases, by="Report date")

combined_count[is.na(combined_count)] = 0
combined_count <- within(combined_count, dth_cumul <- cumsum(death_count))
```

###Combined_count line graph by new cases per month
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
ggplot(combined_count, aes(x=`Report date`)) +
  geom_line(aes(y=confirm_count), color="darkred") +
  #geom_line(aes(y=recovered_count), color="green") +
  geom_line(aes(y=death_count), linetype="twodash")
```

###Combined_count line graph by cumulative cases 
```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
ggplot(combined_count, aes(x=`Report date`)) +
  geom_line(aes(y=conf_cumul), color="darkred") +
  geom_line(aes(y=recov_cumul), color="green") +
  geom_line(aes(y=dth_cumul), linetype="twodash")
```

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
#Count of Reported Confirmed Cases

ggplot(cases_date, aes(x=`Report date`, y=count)) + geom_line() + geom_point() + scale_x_date(date_labels = "%m") + geom_text(aes(label=count), vjust=-0.5)
```

## cases_location

```{r echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
#cases_location$`Last date of residence of the case(s)` <- as.Date(cases_location$`Last date of residence of the case(s)`, "%d/$m/%Y")

num_cases_location <- cases_location %>%
  mutate(count = 0) #%>%
  
```



















